Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-12-15 main.tex
:pencil: Add optimal input distribution

	\begin{section}{Input Distribution, Decision Region, and Precoder Design}
		\begin{subsection}{Primary-backscatter rate region}
			The weighted sum marginal information of tag $q$ associated with symbol $\bar{c}_{i_q}$ and the weighted sum primary-backscatter rate are defined respectively as
			\begin{align}
				I_q(\bar{c}_{i_q};\boldsymbol{y},z)
				& \triangleq \rho I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},q}(\bar{c}_{i_q};z),\label{eq:weighted_sum_marginal_information}\\
				I(c_{\mathcal{K}};\boldsymbol{y},z)
				& \triangleq \rho I_{\mathrm{P}}(c_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(c_{\mathcal{K}};z),\label{eq:weighted_sum_rate}
			\end{align}
			where $\rho \in [0,1]$ denotes the priority of the primary link. To investigate how backscatter modulation and detection may influence the primary transmission, we optimize the input probability distribution, decision region, and transmit precoder to maximize the weighted primary-backscatter sum rate
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{P},\boldsymbol{t},\boldsymbol{w}}}{I}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
				\addConstraint{\sum \nolimits_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.\label{co:average_transmit_power}}
			\end{maxi!}
			where \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} are input probability constraints and \eqref{co:average_transmit_power} is the average transmit power budget. As problem \eqref{op:rate_region} is not jointly convex over $\boldsymbol{P}$, $\boldsymbol{t}$ and $\boldsymbol{w}$, we propose a \gls{bcd} method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
		\end{subsection}

@@

			It suggests that an input probability distribution maximizes the weighted primary-backscatter sum rate if and only if each probable state of each tag produces the same mutual information.
		\end{subsection}

>>>>

	\begin{section}{Input Distribution, Decision Region, and Precoder Design}
		\begin{subsection}{Primary-backscatter rate region}
			The weighted sum marginal information of tag $q$ associated with symbol $\bar{c}_{i_q}$ and the weighted sum primary-backscatter rate are defined respectively as
			\begin{align}
				I_q(\bar{c}_{i_q};\boldsymbol{y},z)
				& \triangleq \rho I_{\mathrm{P},q}(\bar{c}_{i_q};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},q}(\bar{c}_{i_q};z),\label{eq:weighted_sum_marginal_information}\\
				I(c_{\mathcal{K}};\boldsymbol{y},z)
				& \triangleq \rho I_{\mathrm{P}}(c_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(c_{\mathcal{K}};z),\label{eq:weighted_sum_rate}
			\end{align}
			where $\rho \in [0,1]$ denotes the priority of the primary link. To investigate how backscatter modulation and detection may influence the primary transmission, we optimize the input probability distribution, decision region, and transmit precoder to maximize the weighted sum primary-backscatter rate
			\begin{maxi!}
				{\scriptstyle{\boldsymbol{P},\boldsymbol{t},\boldsymbol{w}}}{I}{\label{op:rate_region}}{\label{ob:weighted_sum_rate}}
				\addConstraint{\sum \nolimits_{m_k} P_k(\bar{c}_{m_k})}{=1,\quad\label{co:sum_probability}}{\forall k \in \mathcal{K}}
				\addConstraint{P_k(\bar{c}_{m_k})}{\ge 0,\quad\label{co:nonnegative_probability}}{\forall m_k \in \mathcal{M}, \ \forall k \in \mathcal{K}}
				\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.\label{co:average_transmit_power}}
			\end{maxi!}
			where \eqref{co:sum_probability} and \eqref{co:nonnegative_probability} are input probability constraints and \eqref{co:average_transmit_power} is the average transmit power budget. As problem \eqref{op:rate_region} is not jointly convex over $\boldsymbol{P}$, $\boldsymbol{t}$ and $\boldsymbol{w}$, we propose a \gls{bcd} method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
		\end{subsection}

@@

			It suggests that an input probability distribution maximizes the weighted sum primary-backscatter rate if and only if each probable state of each tag produces the same mutual information. On top of this, we extend the Blahut-Arimoto algorithm and obtain the optimal input probability distribution in closed form as follows.

			\begin{theorem}
				The input probability distribution that achieves the weighted sum primary-backscatter capacity is given by the limit of the following sequence, $\forall i_q \in \mathcal{M}$ and $\forall q \in \mathcal{K}$,
				\begin{equation}
					P_q^{(r+1)}(\bar{c}_{i_q}) = P_q^{(r)}(\bar{c}_{i_q}) \frac{\exp \left( I_q(\bar{c}_{i_q};\boldsymbol{y},z) \right)}{\sum_{m_q} P_q^{(r)}(\bar{c}_{m_q}) \exp \left( I_q(\bar{c}_{m_q};\boldsymbol{y},z) \right)},
				\end{equation}
				where $r \in \mathbb{Z}_+$ is the iteration index and $P_q^{(0)}(\bar{c}_{i_q}) > 0$. [TODO] The probability distribution of tag $q$ is based on the updated probability distribution of tags $1,\ldots,q-1$.
			\end{theorem}
		\end{subsection}
